There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-10 paper/icml_drau/icml_drau.tex
Paper update

The exploration scheme used~\cite{ddpg}, which consists in adding an
\emph{Orhnstein-Ullenbeck}~\cite{orn-ull} process to actions, is naturally time
invariant in the sense that it is first defined as a time continuous stochastic
process, and that discretization of this process are used in practice. Indeed,
a continuous \emph{Orhnstein-Ullenbeck} process is defined as
\begin{equation}
	dx_t = - (x_t - \mu) \theta dt + \sigma \dbt
\end{equation}
and is naturally discretized by turning $d$'s into $\delta$'s, and using
the same $\deltat$ for both the learning algorithm and the exploration scheme.
Consequently, this exploration scheme can readily be used in continuous action
environments.

On the other hand, the usual exploration scheme used in discrete actions
Q-learning, $\varepsilon$-greedy exploration~\cite{sutton} is not time
invariant, in the sense that resulting state trajectories do not converge to a
well defined stochastic process as $\deltat \rightarrow 0$.

\subsection{Learning rates scalings}
\label{subsec:lr}

\subsection{Algorithms}
\label{subsec:algorithm}
We introduce two versions of \emph{Deep Advantage Updating} to cover both the
continuous and discrete action cases. Both relies on applying either DDPG or DQN
to the reparameterized Q-function and enforcing the identifiability of $A^\pi$ by
making sure that $\max_a A^\pi(s, a) = 0$, either approximately or exactly for all
states.
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
\end{algorithm}

\section{Experiments}
\label{sec:exp}

>>>>

The exploration scheme used~\cite{ddpg}, which consists in adding an
\emph{Ornstein-Uhlenbeck}~\cite{orn-uhl} process to actions, is naturally time
invariant in the sense that it is first defined as a time continuous stochastic
process, and that discretization of this process are used in practice. Indeed,
a continuous Ornstein-Uhlenbeck process is defined as
\begin{equation}
	dx_t = - (x_t - \mu) \theta dt + \sigma \dbt
	\label{eq:orn_uhl}
\end{equation}
and is naturally discretized by turning $d$'s into $\delta$'s, and using
the same $\deltat$ for both the learning algorithm and the exploration scheme.
Consequently, this exploration scheme can readily be used in continuous action
environments.

On the other hand, the usual exploration scheme used in discrete actions
Q-learning, $\varepsilon$-greedy exploration~\cite{sutton} is not time
invariant, in the sense that resulting state trajectories do not converge to a
well defined stochastic process as $\deltat \rightarrow 0$. As $\dt$ goes to $0$,
for any $\varepsilon$ independant of $\dt$, the behavior of state trajectories get
closer to that of a white noise.

To obtain a temporally coherent exploration scheme in discrete action environment
when using Q-learning we instead directly apply a discretization of a time continuous
stochastic process to the output of the approximate Q-function, and select actions
by maximizing the resulting perturbed Q-function. Typically, the approximate Q-function
values are also perturbed using a discretized Ornstein-Uhlenbeck noise.

\subsection{Algorithms}
\label{subsec:algorithm}
Two variants of \emph{Deep Advantage Updating} are derived to cover both the continuous
and discrete action cases. They both rely on variants of Q-learning. More precisely,
we learn $V$ and $A$ using approximate version of the following bellman equation
\begin{align}
	V^{\pi}(s) + A^{\pi}(s, a) &= \E_{\delta r \sim \delta r(s, a)}\delta r\nonumber\\ 
				   &+ \gamma^{\deltat}  \E_{\delta s \sim \delta s(s, a)} V^{\pi}(s + \delta s)\label{eq:bellman_A}\\
	A^{\pi}(s, \pi(s)) &= 0\label{eq:max_A}
\end{align}
for a greedy exploitation policy $\pi(s) = \text{argmax}_{a'}A^\pi(s, a')$.
Eq.~\eqref{eq:max_A} is directly verified owing to the parameterization of $A$.
To approximately verify~\eqref{eq:bellman_A}, the corresponding squared residual
is minimized by an approximate gradient descent.
The corresponding update equations when learning from incoming transitions of
an exploratory trajectory are
\begin{align}
	\delta Q_t &= A(s_t, a_t) - \frac{\delta r_t + \gamma^{\deltat} V(s_{t+\deltat}) - V(s_t)}{\deltat}\\
	\theta^1_{t+\deltat} &= \theta^1_t + \eta_1 \partial_{\theta^1} V(s_t) \delta Q_t\\
	\theta^2_{t+\deltat} &= \theta^2_t + \eta_2 \partial_{\theta^2} A(s_t, a_t) \delta Q_t.
	\label{eq:approx_bellman_A}
\end{align}
where $\eta$'s are learning rates. We are now left to derive appropriate learning rates
to provide invariance to time discretization.
\begin{algorithm}[ht]
	\caption{Deep Advantage Updating (Discrete actions)}
	\input{dauc.tex}
\end{algorithm}

\subsection{Learning rates scalings}
\label{subsec:lr}
A necessary condition to guarantee invariance to time discretization is that
the trajectory of the parameters of our function approximators should remain
well behaved when the discretization parameter $\deltat$ decreases. This notably
means that optimization steps should not be too large, in which case parameter
trajectories could diverge in a single gradient step, or two small, in which case
the trajectories would converge to single points as $\deltat$ goes to $0$.
This in turn imposes conditions on the scalings of the learning rates of invariant
algorithms with respect to the discretization timestep.

If we optimize $\theta_1$ and $\theta_2$ according to Eq.~\eqref{eq:approx_bellman_A},
both $\theta_1$ and $\theta_2$ verify update equations of the form
\begin{align}
	\
	\delta \theta^1_t = \eta_1 \partial_{\theta_1} V(s_t) (
\end{align}
To have parameter steps that do not grow larger or shrink to $0$ as $\deltat
\leftarrow 0$, both $\delta \theta^1$ and $\delta \theta^2$ should verify
stochastic differential equations, and notably have a deterministic component
of order $\deltat$. If the deterministic component 
\section{Experiments}
\label{sec:exp}
